% !TeX root = ../thuthesis-example.tex

\newcommand{\authorsign}{
  \begin{table}
    \centering
    \normalsize
    % \vspace{12pt}
    \begin{tabular}{llll}
    Signature: & \hspace{4cm} & Date: &  \hspace{4cm}
    \end{tabular}
  \end{table}
}
\newcommand{\authorsupervisorsign}{
  \begin{table}
    \centering
    \normalsize
    % \vspace{12pt}
    \begin{tabular}{llll}
    Signature of Author: & \hspace{4cm} & Date: &  \hspace{4cm}\\
    Signature of Supervisor: & \hspace{4cm} & Date: &  \hspace{4cm}
    \end{tabular}
  \end{table}
}

\begin{statementcopyright}
  \section*{Declaration of Originality of Thesis}
  \vspace{1em}

  % \begin{spacing}{1.25}
    I hereby declare that this dissertation is my own original work under the guidance of my supervisor. It does not contain any research results that others have published or written. All sources I quoted in the dissertation are indicated in references or have been indicated or acknowledged. I shall bear the legal liabilities of the above statement.
  % \end{spacing}

  \authorsign

  \section*{Declaration of Authorization of Thesis}

  \vspace{1em}

  % \begin{spacing}{1.25}
    I fully understand the regulations regarding the collection, retention and use of thesis and dissertations of Southern University of Science and Technology.
    \begin{enumerate}
      \item Submit the electronic version of thesis and dissertation as required by the University.
      \item The University has the right to retain and send the electronic version to other institutions that allow the dissertation to be read by the public.
      \item The University may save all or part of the dissertation in certain databases for retrieval, and may save it with digital, cloud storage or other methods for the purpose of teaching and scientific research. I agree that the full text of the dissertation can be viewed online or downloaded within the campus network.
      \begin{enumerate}[label={\arabic*)}]
        \item I agree that in the year of the submission, the dissertation can be retrieved online and the first 16 pages can be previewed within the campus network.
        \item I agree that $\mdlgwhtsquare$ in the year of the dissertation submission $\mdlgwhtsquare$ one year later, the full text of the dissertation is to be viewed online or downloaded by the public.
      \end{enumerate}
      \item This authorization applies to decrypted confidential dissertations.
    \end{enumerate}

  % \end{spacing}

  \authorsupervisorsign

\end{statementcopyright}